---
title: "Fruity_Exp1_Analysis_online"
author: "Lauren Oey"
date: "12/3/2018"
output: pdf_document
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)

df <- read.csv("raw.csv")
glimpse(df)
```

```{r}
(n <- length(levels(df$subjID)))
```

```{r}
catch <- c("spiky artichoke",
           "sweet beet",
           "salty plaintain",
           "green grape",
           "dark ripe avocado",
           "bitter sweet okra")

df.exclCrit <- df %>%
  filter(stimType == "stimFillList") %>%
  mutate(correct = ifelse(produce %in% catch, as.character(recode(produce,"spiky artichoke" = "spiky",
  "sweet beet" = "sweet",
  "salty plaintain" = "salty",
  "green grape" = "green",
  "dark ripe avocado" = "ripe",
  "bitter sweet okra" = "bitter")), NA)) %>%
  filter(!is.na(correct)) %>%
  group_by(subjID) %>%
  summarise(propCorrect = sum(selectedTxt == correct) / n())

ggplot(df.exclCrit, aes(x=propCorrect)) +
  geom_bar() +
  ggtitle("Distribution on Catch Trials") +
  scale_x_continuous("Prop of Correct Performance by Subject", limits = c(0,1.1)) +
  theme_minimal()
```

```{r}
subj.excluded <- df.exclCrit %>%
  filter(propCorrect < 0.8) %>%
  .$subjID ;subj.excluded
length(subj.excluded)

df.final <- df %>%
  filter(!subjID %in% subj.excluded & stimType != "stimFillList")

df_lm <- df.final %>%
  mutate(structureGroup = as.factor(ifelse(structureIndex %in% c("a","b"), "ab", "cd")),
         adjFirst.alph = ifelse(as.character(adjFirst) < as.character(adjSecond), as.character(adjFirst), as.character(adjSecond)),
         adjSecond.alph = ifelse(as.character(adjFirst) > as.character(adjSecond), as.character(adjFirst), as.character(adjSecond)),
         adjPairing.alph = paste0(adjFirst.alph, "_", adjSecond.alph),
         adjSelected.isAlph = as.numeric(as.character(selectedTxt) == as.character(adjFirst.alph)),
         syntOrder.alph = ifelse(adjFirst == adjFirst.alph, "alphOrder.true", "alphOrder.false"))
```

```{r}
df1 <- df.final %>%
  filter(structureIndex %in% c("c","d")) %>%
  group_by(as.factor(stimType)) %>%
  mutate(selectedTxt.l.adj2 = as.numeric(as.character(selectedTxt) == as.character(adjSecond))) %>%
  group_by(stimType, subjID) %>%
  summarise(percAdj2.subj = sum(selectedTxt.l.adj2) / n())

summary1 <- df1 %>%
  group_by(stimType) %>%
  summarise(prop = mean(percAdj2.subj),
            se = sqrt(prop*(1-prop)/n),
            lower = max(prop - 1.96*se, 0),
            upper = min(prop + 1.96*se, 1))

df1 %>%
  ggplot(aes(x=stimType)) +
  geom_dotplot(aes(y=percAdj2.subj),binaxis="y",stackdir="center", fill="blue", alpha=0.5) +
  geom_pointrange(data=summary1, aes(x=stimType, y = prop, ymin=lower, ymax=upper), colour="darkblue") +
  geom_errorbar(data=summary1, aes(x=stimType, ymin=lower, ymax=upper), width=0.2) +
  ggtitle(bquote("Proportion of"*~A[2]*" Choices in"*~A[1]*" for a"~A[2]*" N by Scale (Control)")) +
  scale_x_discrete("Scale", labels=c("Same Scale", "Different Scale")) +
  scale_y_continuous(bquote("Prop of"*~A[2]*" Chosen"), limits=c(0,1)) +
  geom_hline(yintercept=0.5, linetype=2) +
  theme_minimal()
ggsave("img/Results_periphrastic.png")
```

```{r}
df2 <- df.final %>%
  filter(structureIndex %in% c("a","b")) %>%
  group_by(as.factor(stimType)) %>%
  mutate(selectedTxt.l.adj2 = as.numeric(as.character(selectedTxt) == as.character(adjSecond))) %>%
  group_by(stimType, subjID) %>%
  summarise(percAdj2.subj = sum(selectedTxt.l.adj2) / n())

summary2 <- df2 %>%
  group_by(stimType) %>%
  summarise(prop = mean(percAdj2.subj),
            se = sqrt(prop*(1-prop)/n),
            lower = max(prop - 1.96*se, 0),
            upper = min(prop + 1.96*se, 1))

df2 %>%
  ggplot(aes(x=stimType)) +
  geom_dotplot(aes(y=percAdj2.subj),binaxis="y",stackdir="center", fill="blue", alpha=0.5) +
  geom_pointrange(data=summary2, aes(y = prop, ymin=lower, ymax=upper), colour="darkblue") +
  geom_errorbar(data=summary2, aes(ymin=lower, ymax=upper), width=0.2) +
  ggtitle(bquote("Proportion of"*~A[2]*" Choices in"*~A[1]*~A[2]*" N by Scale (Test)")) +
  scale_x_discrete("Scale", labels=c("Same Scale", "Different Scale")) +
  scale_y_continuous(bquote("Prop of"*~A[2]*" Chosen"), limits=c(0,1)) +
  geom_hline(yintercept=0.5, linetype=2) +
  theme_minimal()
ggsave("img/Results_double.png")
```

```{r}
df3 <- df.final %>%
  mutate(selectedTxt.l.adj2 = as.numeric(as.character(selectedTxt) == as.character(adjSecond)),
         structureGroup = ifelse(structureIndex %in% c("a","b"), "ab", "cd")) %>%
  group_by(structureGroup, subjID) %>%
  summarise(percAdj2.subj = sum(selectedTxt.l.adj2) / n())

summary3 <- df3 %>%
  group_by(structureGroup) %>%
  summarise(prop = mean(percAdj2.subj),
            se = sqrt(prop*(1-prop)/n),
            lower = max(prop - 1.96*se, 0),
            upper = min(prop + 1.96*se, 1))

df3 %>%
  ggplot(aes(x=structureGroup)) +
  geom_dotplot(aes(y=percAdj2.subj),binaxis="y",stackdir="center", fill="blue", alpha=0.5) +
  geom_pointrange(data=summary3, aes(y = prop, ymin=lower, ymax=upper), colour="darkblue") +
  geom_errorbar(data=summary3, aes(ymin=lower, ymax=upper), width=0.2) +
  ggtitle(bquote("Proportion of"*~A[2]*" Choices by Syntax")) +
  scale_x_discrete("Syntactic Structure", labels=c(bquote(~A[1]*~A[2]*" N"), bquote(~A[1]*" for a"~A[2]*" N"))) +
  scale_y_continuous(bquote("Prop of"*~A[2]*" Chosen"), limits=c(0,1.05)) +
  geom_hline(yintercept=0.5, linetype=2) +
  theme_minimal()
ggsave("img/Results_bySyntax.png")
```


Full Model w/ Interaction between Adjective Ordering, Syntactic Structure, and Scale Dimensionality

Dependent measure is binary, in which selected text == alphabetically first adjective (alphabetical anchoring)

Adjective Ordering (syntOrder.alph) refers to whether the alphabetically first adjective is the first or second adjective in terms of word ordering

Syntactic Structure (structureGroup) refers to whether the sentence takes the form "Adj1 for a Adj2 N" or "Adj1 Adj2 N"

Scale Dimensionality (stimType) refers to whether the two adjectives are on the same scale or different scales

Random intercepts for subject and stimulus (noun)

Full model has a significant effect of word ordering (as predicted), slight signif effect of syntactic structure and signif interaction between word ordering and syntactic structure


```{r}
model <- glmer(cbind(adjSelected.isAlph, 1-adjSelected.isAlph) ~ syntOrder.alph * structureGroup * stimType  + (1 | subjID) + (1 | produce),
               data=df_lm, family="binomial")
summary(model)
```

```{r}
model2 <- glmer(cbind(adjSelected.isAlph, 1-adjSelected.isAlph) ~ syntOrder.alph + (1 | subjID) + (1 | produce),
               data=df_lm, family="binomial")
summary(model2)
```

This is the model that should be reported. It just shows adjective ordering and syntactic structure and their interaction are significant predictors of selection.

```{r}
contrasts(df_lm$structureGroup) <- contr.sum(2)

model3 <- glmer(cbind(adjSelected.isAlph, 1-adjSelected.isAlph) ~ syntOrder.alph * structureGroup + (1 | subjID) + (1 | produce),
               data=df_lm, family="binomial")
summary(model3)
```

```{r}
df.final %>%
  mutate(selectedTxt.l.adj2 = as.numeric(as.character(selectedTxt) == as.character(adjSecond))) %>%
  group_by(produce, stimType) %>%
  summarise(percAdj2.subj = sum(selectedTxt.l.adj2) / n()) %>%
  ggplot(aes(x=percAdj2.subj, fill=stimType)) +
  geom_density(alpha = 0.5) +
  ggtitle("Distribution of Selection by Noun") +
  scale_fill_discrete(labels=c("Same Scale", "Different Scale")) +
  scale_x_continuous(bquote("Prop of"*~A[2]*" Chosen"), limits=c(0,1)) +
  scale_y_continuous("Density") +
  theme_minimal()
```
