---
title: "Fruity_Exp2_Analysis"
author: "Lauren Oey"
date: "11/1/2018"
output: pdf_document
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)

df <- read.csv("raw.csv")

df <- df %>%
  mutate(order = as.factor(recode(as.character(order), "1"="adj1_adj2", "2"="adj2_adj1")),
         prosody = as.factor(recode(as.character(prosody), "1"="adj1", "2"="adj2")))
glimpse(df)
```

```{r}
(n <- length(levels(df$subjID)))
```

```{r}
catch <- c("spiky artichoke",
           "sweet beet",
           "salty plaintain",
           "green grape",
           "dark ripe avocado",
           "bitter sweet okra")

df.exclCrit <- df %>%
  filter(stimType == "stimFillList") %>%
  mutate(correct = ifelse(produce %in% catch, as.character(recode(produce,
                                                                  "spiky artichoke" = "spiky",
                                                                  "sweet beet" = "sweet",
                                                                  "salty plaintain" = "salty",
                                                                  "green grape" = "green",
                                                                  "dark ripe avocado" = "ripe",
                                                                  "bitter sweet okra" = "bitter")), NA)) %>%
  filter(!is.na(correct)) %>%
  group_by(subjID) %>%
  summarise(propCorrect = sum(selectedTxt == correct) / n())

ggplot(df.exclCrit, aes(x=propCorrect)) +
  geom_bar() +
  ggtitle("Distribution on Catch Trials") +
  scale_x_continuous("Prop of Correct Performance by Subject", limits = c(0,1.1)) +
  theme_minimal()
```

```{r}
subj.excluded <- df.exclCrit %>%
  filter(propCorrect < 0.8) %>%
  .$subjID ;subj.excluded
length(subj.excluded)

df.final <- df %>%
  filter(!subjID %in% subj.excluded & stimType != "stimFillList")

df_lm <- df.final %>%
  mutate(structureGroup = as.factor(ifelse(structureIndex %in% c("a","b"), "ab", "cd")),
         adjFirst.alph = ifelse(as.character(adjFirst) < as.character(adjSecond), as.character(adjFirst), as.character(adjSecond)),
         adjSecond.alph = ifelse(as.character(adjFirst) > as.character(adjSecond), as.character(adjFirst), as.character(adjSecond)),
         adjPairing.alph = paste0(adjFirst.alph, "_", adjSecond.alph),
         adjSelected.isAlph = as.numeric(as.character(selectedTxt) == as.character(adjFirst.alph)),
         syntOrder.alph = ifelse(adjFirst == adjFirst.alph, "alphOrder.true", "alphOrder.false"))
```
```{r}
df2 <- df_lm %>%
  group_by(prosody, subjID) %>%
  summarise(percAdj2.subj = sum(as.numeric(as.character(selectedTxt) == as.character(adjSecond))) / n())

summary2 <- df2 %>%
  group_by(prosody) %>%
  summarise(prop = mean(percAdj2.subj),
            se = sqrt(prop*(1-prop)/n),
            lower = max(prop - 1.96*se, 0),
            upper = min(prop + 1.96*se, 1))

df2 %>%
  ggplot(aes(x=as.factor(prosody))) +
  geom_dotplot(aes(y=percAdj2.subj),binaxis="y",stackdir="center", fill="blue", alpha=0.5) +
  geom_pointrange(data=summary2, aes(y = prop, ymin=lower, ymax=upper), colour="darkblue") +
  geom_errorbar(data=summary2, aes(ymin=lower, ymax=upper), width=0.2) +
  ggtitle(bquote("Proportion of"*~A[2]*" Choices in"*~A[1]*~A[2]*" N")) +
  scale_x_discrete("Prosody", labels=c("Adj1", "Adj2")) +
  scale_y_continuous(bquote("Prop of"*~A[2]*" Chosen"), limits=c(0,1)) +
  geom_hline(yintercept=0.5, linetype=2) +
  theme_minimal()
ggsave("img/Results_prosody.png")
```


Full Model w/ Interaction between Adjective Ordering, Prosody, and Scale Dimensionality

Dependent measure is binary, in which selected text == alphabetically first adjective (alphabetical anchoring)

Adjective Ordering (syntOrder.alph) refers to whether the alphabetically first adjective is the first or second adjective in terms of word ordering

Prosody (prosody) refers to which adjective has a prosodic emphasis

Scale Dimensionality (stimType) refers to whether the two adjectives are on the same scale or different scales

Random intercepts for subject and stimulus (noun)

Full model has a significant effect of word ordering (as predicted), slight signif effect of syntactic structure and signif interaction between word ordering and syntactic structure


```{r}
model <- glmer(cbind(adjSelected.isAlph, 1-adjSelected.isAlph) ~ syntOrder.alph * prosody * stimType  + (1 | subjID) + (1 | produce),
               data=df_lm, family="binomial")
summary(model)
```

This is the model that should be reported. It shows adjective ordering and prosody and their interaction are significant predictors of selection.

```{r}
model2 <- glmer(cbind(adjSelected.isAlph, 1-adjSelected.isAlph) ~ syntOrder.alph * prosody + (1 | subjID) + (1 | produce),
               data=df_lm, family="binomial")
summary(model2)
```

